A meta-analysis of mental rotation ability in the first years of life

### 2022-04-22 code/analysis.Rmd
Add meta-regression plot

# Compute standard error of Cohen's d based on assumed correlation
# See Hedges' formula on p. 253 in http://dx.doi.org/10.20982/tqmp.14.4.p242
# This will need a sensitivity analysis regarding the values of `r_assumed`
r_assumed <- 0.5
dat_all %>%
  mutate(
    ni = sample_size,
    vi = (dfi / (dfi - 2)) * ((2 * (1 - r_assumed)) / ni) *
      (1 + gi^2 * (ni / (2 * (1 - r_assumed)))) - (gi^2 / ji^2),
    sei = sqrt(vi)
  ) %>%
  filter(!is.na(gi)) %>%
  select(
    article,
    group,
    experiment,
    gender_split,
    gi,
    ni,
    vi,
    sei,
    female_percent,
    age_mean
  ) -> dat_all_r

@@

  # Gender as a categorical variable
  gender = case_when(
    female_percent == 1.0 ~ "female",
    female_percent == 0.0 ~ "male",
    TRUE ~ "mixed"
  ) %>% factor(levels = c("mixed", "female", "male")),

  # Mean sample age in months, centered around the mean
  age = age_mean / 30.417,
  age = age - mean(age, na.rm = TRUE),
  .keep = "unused"

) -> dat
```

@@

# Meta-regression with age
res_age <- rma.mv(
  gi, vi,
  mods = ~age,
  random = ~ 1 | article / experiment,
  data = dat,
  slab = experiment
)
print(res_age)
# forest(res_age)

# Meta-regression with gender, age, and their interaction
res_full <- rma.mv(
  gi, vi,
  mods = ~ gender * age,
  random = ~ 1 | article / experiment,
  data = dat,
  slab = experiment
)
print(res_full)
# forest(res_full)
```

>>>>

# Compute standard error of Cohen's d based on assumed correlation
# See Hedges' formula on p. 253 in http://dx.doi.org/10.20982/tqmp.14.4.p242
# This will need a sensitivity analysis regarding the values of `r_assumed`
r_assumed <- 0.5
dat_all %>%
  mutate(
    ni = sample_size,
    vi = (dfi / (dfi - 2)) * ((2 * (1 - r_assumed)) / ni) *
      (1 + gi^2 * (ni / (2 * (1 - r_assumed)))) - (gi^2 / ji^2),
    sei = sqrt(vi)
  ) %>%
  filter(!is.na(gi)) %>%
  select(
    article,
    group,
    experiment,
    gender_split,
    gi,
    ni,
    vi,
    sei,
    female_percent,
    age_mean,
    age_sd,
    age_min,
    age_max
  ) -> dat_all_r

@@

    # Gender as a categorical variable
    gender = case_when(
      female_percent == 1.0 ~ "Female",
      female_percent == 0.0 ~ "Male",
      TRUE ~ "Mixed"
    ) %>% factor(levels = c("Mixed", "Female", "Male")),

    # Mean sample age in months, centered around the mean
    age = age_mean / 30.417,
    age_c = age - mean(age, na.rm = TRUE),
    age_sd = age_sd / 30.417,
    .keep = "unused"
  ) -> dat
```

@@

# Meta-regression with age
res_age <- rma.mv(
  gi, vi,
  mods = ~age_c,
  random = ~ 1 | article / experiment,
  data = dat,
  slab = experiment
)
print(res_age)
# forest(res_age)

# Meta-regression with gender, age, and their interaction
res_full <- rma.mv(
  gi, vi,
  mods = ~ gender * age_c,
  random = ~ 1 | article / experiment,
  data = dat,
  slab = experiment
)
print(res_full)
# forest(res_full)
```

```{r, fig_regression}
# Plot regression with gender and age
alph <- 0.7
dat %>%
  ggplot(aes(x = age, y = gi, color = gender)) +
  # Data points
  # geom_errorbar(aes(xmin = age - age_sd, xmax = age + age_sd), alpha = alph) +
  # geom_errorbar(aes(ymin = gi - sei, ymax = gi + sei), alpha = alph) +
  geom_point(aes(size = ni), shape = 16, alpha = alph) +
  # Regression lines - currently not reflecting the meta-analytic model
  geom_smooth(method = lm, formula = y ~ x, alpha = .1) +
  # Styling
  scale_x_continuous(limits = c(3, 16), breaks = seq(4, 16, 2)) +
  scale_y_continuous(limits = c(-1.3, 2.5), breaks = seq(-1, 2.5, 0.5)) +
  scale_color_brewer(palette = "Dark2") +
  labs(
    x = "Age (months)",
    y = expression("Hedges'" ~ italic("g")),
    color = "Gender",
    size = "Sample size"
  ) +
  theme_bw() +
  theme(
    panel.border = element_rect(size = 1),
    panel.grid = element_line(color = "grey90"),
    text = element_text(family = "Helvetica"),
  )

# Save the plot
ggsave(here(figures_dir, "regression.pdf"), width = 7, height = 4)
```
